Machine Learning for Handwriting Recognition: Algorithms and Techniques

### 2023-11-14 Manuscript/Manuscript.tex
General Commits - Adding Figure, Formulas, and Code Block

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{lipsum}
\usepackage{setspace}
\usepackage{tikz}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\doublespacing
\title{Machine Learning for Handwriting Recognition: Algorithms and Techniques}
\author{Lai Jiang\\
  University of Connecticut Department of Statistics
}

@@

\paragraph{Neural Network Approaches}
Although there are many ways to emphasize and implement the machine learning and training process, the most common way that related to neural network could be elaborated like this: For example, if we have a hand-written number, say 7, in this case, how should we let the machine know it is 7? In the MNIST Dataset, all pictures in it are 5 to 5 scaled, which means there are 25 pixels in total. And then we can line them up into a one-dimensional column, and label them 0 if the block or pixel is black, and 1 when this block is white. In order to proceed to the next step, we also need to number them from $X^{0}_{0}$ to $X^{0}_{24}$. The top number refers to the number of layers and the lower number refers to the number of the elements, and in this case, it is refers to every single pixel.

@@

\section*{Further Improvements}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{lipsum}
\usepackage{setspace}
\usepackage{tikz}
\usepackage{pdfpages}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\doublespacing
\title{Machine Learning for Handwriting Recognition: Algorithms and Techniques}
\author{Lai Jiang\\
  University of Connecticut Department of Statistics
}

@@

\paragraph{Neural Network Approaches}
Although there are many ways to emphasize and implement the machine learning and training process, the most common way that related to neural network could be elaborated like this: For example, if we have a hand-written number, say 7, in this case, how should we let the machine know it is 7? In the MNIST Dataset, all pictures in it are 5 to 5 scaled, which means there are 25 pixels in total. And then we can line them up into a one-dimensional column, and label them 0 if the block or pixel is black, and 1 when this block is white. In order to proceed to the next step, we also need to number them from $X^{0}_{0}$ to $X^{0}_{24}$. The top number refers to the number of layers and the lower number refers to the number of the elements, and in this case, it is refers to every single pixel.Blow is a figure of a complete computing process of handwriting recognition.
\vspace{10pt}
\includegraphics[page = 1, width=\linewidth]{Neural Networks Exemplar.pdf}

@@

\section*{Code Block}
\begin{verbatim}
#include <stdio.h>
int main() {
   printf("Hello, World!");
   return 0;
}
\end{verbatim}
